Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-27 index.qmd
add results

@@

  total <- read.csv( "Data/Resampled_saved_data_total.csv")

@@

@@

(plot <- ggplot(NewData)+
  geom_ribbon(aes(x = sqrt(area), y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = sqrt(area), y = fit,
                color = true_fct, group = true_fct
                ))+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm")
          )

@@

@@

>>>>

To assess the impact of spatial resolution on the model's output, the reflectance of each flight's orthomosaic was spatially resampled using the average method from the Terra package in R. DISCOV was then applied to these resampled rasters. The results were compared to the original model predictions, which were resampled using the mode method from the Terra package in R. For each resolution and each class of the model, an agreement percentage was obtained, where a score of 100 indicates that all pixels in the two products are identical, and a score of 0 indicates that all pixels are different.

We used a Generalized Linear Model (GLM) with a Gaussian family and an identity link function to investigate the relationship between pixel resolution, vegetation class, and their interaction on the response variable, the agreement. The formula for the model was:

$$
Agreement \sim  Resolution \times VegetationClass
$$ {#eq-gam}

@@

  total <- read.csv( "Data/Resampled_saved_data_total.csv") %>% 
    mutate(true_fct = as.factor(true))

@@

# validation <- read.csv( "Data/Resampled_saved_data.csv")

@@

(plot <- ggplot(NewData)+
  geom_ribbon(aes(x = sqrt(area)/100, y = fit, ymax = fit+se, ymin = fit-se, 
                  color = true_fct, group = true_fct, fill = true_fct
                  ), alpha = 0.2)+
  geom_line(aes(x = sqrt(area)/100, y = fit,
                color = true_fct, group = true_fct
                ))+
      scale_fill_manual(name = NULL,
                        values = cols_fill,
                        labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water")) +
    scale_color_manual(name = NULL,
                      values = cols_fill,
                      labels = c("Green algae", "Seagrass", "Brown algae", "Red algae", "Sediment", "Sunglint","Water"))+
  theme_Bede()+
  xlab("Resolution (m)") +
  ylab("Agreement")+
  theme(axis.title = element_text(size = 20),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 15),
        legend.key.size = unit(1, "cm")
          )

@@

@fig-pixelsize shows an effect of the pixel size on the agreement between the two products. The highest resolution in which the resampling has been performed is 10 cm. At this resolution, the agreement has already decreased from 78% (red algae) to 94% (seagrass), depending on the class. As pixel size increases, the agreement between the products declines steadily for all classes. This decline is most pronounced for green algae, which experiences the sharpest drop in agreement as pixel size increases beyond 10 m, reaching below 0% at a pixel size of 30 m. Seagrass maintain higher levels of agreement at coarser resolutions, although a clear decline is still observed, with seagrasses dropping from over 94% at 10 cm to around 88% at 30 m. Brown algae and red algae show a more moderate decline compared to red algae, with agreement levels remaining around 62% and 40%, respectively, at 30 m resolution.

@@

The Generalized Linear Model (GLM) analysis revealed a significant effect of pixel resolution on the agreement, with a negative relationship ($$\beta = -1.0334 \times 10^{-8}, p < 0.001$$). This indicates that as pixel resolution increases, the proportion of the response variable decreases.

The vegetation classes also exhibited distinct effects on the agreement. Magnoliopsida showed a significant positive effect ($$\beta = 0.1202, p < 0.001$$), suggesting that this class was associated with a higher agreement.
